The implementation is local-first but preserves GPU-ready command contracts.
The early MVP used tiny GPT-2 and GPT-2 LoRA smoke runs to validate the harness.
The current active GPU lane uses Qwen3-0.6B with LoRA adapters on two V100 16GB GPUs.

\paragraph{Datasets.}
The local harness uses a TOFU-style synthetic biography fixture with a forget split and retain split.
Each forget item has prompt variants, a target answer, aliases where available, and a neutral answer.

\paragraph{Threshold calibration.}
Thresholds are calibrated from a retain-only oracle checkpoint.
The evaluator stores quantiles $q90$, $q95$, and $q99$ with global threshold $\tau_{\mathrm{global}}=0$.
The default reported metric uses $q95$.

\paragraph{Baselines.}
Implemented baselines include gradient ascent with retain CE, NPO, strong NPO, NPO with paraphrases, syntactic diversification, and immediate-matched constrained gradient ascent.
The decisive Qwen comparison currently uses constrained gradient ascent because Strong NPO did not reach HLC's immediate forget level in the Qwen sweep.

\paragraph{HLC variants.}
The draft covers K1/K2 GPT-2 smoke variants, prior K2/K4 local stress diagnostics, and the active Qwen K4 stress-tuned candidate.
The final Qwen K4 long-horizon table is pending seeded rerun completion.

\paragraph{Reproducibility.}
The survival evaluator writes CSV and JSONL artifacts for each horizon, including survival curves, retain utility, resurrection examples, and generation logs.
All result tables in this draft should be traceable to `runs/reports/` artifacts.
