This section is split into locked local diagnostics and pending Qwen results.

\subsection{Benign Curves Overstate HLC Durability}

On benign relearn pools, HLC-SG appeared strongest in the local MVP.
It had the lowest immediate resurrection and highest benign survival AUC.
This result motivated the stricter conditional protocol.

\input{tables/benign_main_track}

\subsection{Answer-Bearing Stress Changes the Conclusion}

Under immediate-matched answer-bearing stress, current HLC variants did not beat the strongest local baselines.
The held-out stress table is the clearest locked diagnostic result.

\input{tables/heldout_stress}

\subsection{GPT-2 LoRA Smoke Confirms the Larger-Model Path}

The GPT-2 LoRA lane validates the training and evaluation path but does not establish a method win.
K2 improves some short-horizon signals over K1, but still trails Strong NPO by $t=128$.

\input{tables/gpt2_long}

\subsection{Qwen3-0.6B Seeded Long-Horizon Gate}

The Qwen3-0.6B lane is the active decision gate for a tuned HLC K4 candidate against immediate-matched constrained gradient ascent.
The unseeded/provisional long-512 result should not be used for paper claims.
The seeded rerun must populate this table.

\input{tables/qwen_pending}

\paragraph{Current interpretation.}
If tuned HLC beats matched gradient ascent on conditional resurrection or conditional AUC after the seeded rerun, the paper can include a positive Qwen diagnostic result.
If it loses, the paper should remain a rigorous negative result centered on the evaluation protocol.
